---
title       : Tommy John Surgery Pitching Statistics
subtitle    : Pitchers who have undergone the Surgery once inbetween 2005-2015
author      : Matt Lutz
job         : DevDataProdProject
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []         # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## What is Tommy John Surgery?

-"Tommy John surgery (TJS), known in medical practice as ulnar collateral ligament (UCL) reconstruction, is a surgical graft procedure in which the ulnar collateral ligament in the medial elbow is replaced with a tendon from elsewhere in the body." 

-"The UCL can become stretched, frayed, or torn through the repetitive stress of the throwing motion. The risk of injury to the throwing athlete's ulnar collateral ligament of elbow joint is thought to be extremely high as the amount of stress through this structure approaches its ultimate tensile strength during a hard throw." -Wikipedia

--- .class #id 

## Importance

-Tommy John Surgery causes pitchers to miss a season or more of their career

-Teams factor these players into their future plans

-Players lose large amounts of their

-A large number of young, starting pitchers are having the surgery

-Delves into which statistics are diminished due to surgery, able to spot trends

-Investigates the preceived theory that pitchers do not lose a "step" after the surgery

--- .class #id

## App Description

-The Tommy John App is a compilation of statistics over the past 10 years

-Interactive and cutsomizable rChart - faceted by before and after their surgery.
  1. Look at all pitchers or individual pitchers
  2. Statistics on velocity & performance over different seasons
  3. Axis Adjustment
  4. Interactivity on rChart displaying pitcher/statistic

-Those included are pitchers who have had pitching statistics before and after their surgery over that timespan.

-Excluded are pitchers who have had surgery twice or more.
  

--- .class #id 

## Pitchers Before vs After Tommy John - Velocity
```{r TJ, echo=FALSE, cache= TRUE}
TJ <- read.csv("C:/Users/Matt/Desktop/DataProj/AggStats.csv")
TJ <- TJ[,-1]
suppressPackageStartupMessages(library(dplyr))
TJBefore <- filter(TJ, Surgery == "Before")
TJAfter <- filter(TJ, Surgery == "After")
```
Fastball 
Before:
```{r Fastball, echo = FALSE}
##Before
summary(TJBefore$FastballVelocity)
```
After:
```{r FastballAfter, echo = FALSE}
##Before
summary(TJAfter$FastballVelocity)
```

--- .class #id 

## Pitchers Before vs After Tommy John - Velocity
Changeup
Before:
```{r Changeup, echo=FALSE}
##Before
summary(TJBefore$ChangeupVelocity)
```
After:
```{r Changeup2, echo=FALSE}
##After
summary(TJAfter$ChangeupVelocity)
```

--- .class #id 

























